Analysis of HTTPS Adoption and Third-party Tracking: \\A Swedish Perspective

### 2015-05-02 paper/figures.tex
Replace trimmed pdf figures with new figures in the right size

\nextgroupplot[
	title=(a) Origin HTTP response codes,
	allDatasetsStackedXbar,
	allDatasetsXbar,
	allDatasetsXbarMiniResults,
	yticklabels={},
]

@@

\nextgroupplot[
	title=(b) Origin redirects,
	allDatasetsStackedXbar,
	allDatasetsXbar,
	allDatasetsXbarMiniResults,
	yticklabels={},
	legend columns=2,
]

@@

\nextgroupplot[
	title=(c) Resource security,
	allDatasetsStackedXbar,
	allDatasetsXbar,
	allDatasetsXbarMiniResults,
	yticklabels={Top 10k global,Top 10k global (HTTPS), Top 10k .se,Top 10k .se (HTTPS),Rand 100k .se,Rand 100k .se (HTTPS),Municipal .se,Municipal .se (HTTPS)},
]

@@

\tikzsetnextfilename{mini-2x2-categories-organizations}
\begin{tikzpicture}
\begin{groupplot}[
	group style={
		group size=2 by 4,
		horizontal sep=8pt,
		vertical sep=16pt,
	},
]

>>>>

\nextgroupplot[
	% title=(a) Origin HTTP response codes,
	allDatasetsStackedXbar,
	allDatasetsXbar,
	allDatasetsXbarMiniResults,
	yticklabels={},
]

@@

\nextgroupplot[
	% title=(b) Origin redirects,
	allDatasetsStackedXbar,
	allDatasetsXbar,
	allDatasetsXbarMiniResults,
	yticklabels={},
	legend columns=2,
]

@@

\nextgroupplot[
	% title=(c) Resource security,
	allDatasetsStackedXbar,
	allDatasetsXbar,
	allDatasetsXbarMiniResults,
	yticklabels={Top 10k global,Top 10k global (HTTPS), Top 10k .se,Top 10k .se (HTTPS),Rand 100k .se,Rand 100k .se (HTTPS),Municipal .se,Municipal .se (HTTPS)},
]

@@

\tikzsetnextfilename{mini-2x2-categories-organizations-ybar}
\begin{tikzpicture}
\begin{groupplot}[
	group style={
		group size=2 by 4,
		horizontal sep=8pt,
		vertical sep=16pt,
	},
]

### 2015-05-02 paper/paper.tex
Use unix line endings
Replace trimmed pdf figures with new figures in the right size

\begin{figure*}[t]
\centering
\includegraphics[width=0.98\textwidth]{paperFigs-figure0.pdf}
\begin{tabular}{ccc}
(a) Origin response code &
(b) Origin redirect &
(c) Resource breakdown \\
\end{tabular}
\caption{Example domain categories and their original responses, 
redirects, and HTTPS usage for individual resource transfers.}
\label{fig:httpsDiff}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure*}[t]
%% trim = l b r t
\includegraphics[trim=0mm 47mm 0mm 56mm, clip, width=0.98\textwidth]{figures-figure16.pdf}
\includegraphics[trim=0mm 0mm 0mm 106mm, clip, width=0.98\textwidth]{figures-figure16.pdf}
\caption{Secure connections for succesful connections when trying to use HTTPS.
(Note that the majority of websites (as per Figure~\ref{fig:httpsDiff}) do not respond.)}
\label{fig:https}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure*}[t]
%% trim = l b r t
\includegraphics[trim=0mm 0mm 0mm 56mm, clip, width=0.98\textwidth]{figures-figure16.pdf}
\caption{Secure connections for succesful HTTPS attempts (top row)
and HTTP attempts (bottom row).
(Note that the majority of websites does not respnd to HTTPS (as per Figure~\ref{fig:httpsDiff}).)}
\label{fig:https2}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure}[t]
%% trim = l b r t
\includegraphics[trim=0mm 0mm 92mm 0mm, clip, width=0.31\textwidth]{paperFigs-figure2.pdf}
\includegraphics[trim=112mm 0mm 0mm 0mm, clip, width=0.16\textwidth]{paperFigs-figure2.pdf}
\caption{External third-party resource usage.}
\label{fig:external}
\vspace{-0pt}
\end{figure}

@@

%%INSERT FIGURES (a) and (b) FROM THIS MORNINGS FIGURES ...
\begin{figure*}[t]
%% trim = l b r t
\includegraphics[trim=0mm 73mm 0mm 0mm, clip, width=0.98\textwidth]{figures-figure16.pdf}
\includegraphics[trim=0mm 0mm 0mm 106mm, clip, width=0.98\textwidth]{figures-figure16.pdf}
\caption{Domain covererage of different categories of known tracker services (top row)
and companies (bottom row), as per Disconnect's blocking list.}
\label{fig:categories-companies}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure}[t]
%% trim = l b r t
\centering
\includegraphics[width=0.48\textwidth]{figures-figure17.pdf}
\begin{tabular}{cc}
(a) Sweden &
(b) Global \\
\end{tabular}
\caption{Correlation of tracker coverage seen with HTTP and HTTPS.}
\label{fig:scatter}
\vspace{-0pt}
\end{figure}

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.98\textwidth]{figures-mini-3x1-status-redirects-secure-xbar.pdf}
\begin{tabular}{ccc}
(a) Origin response code &
(b) Origin redirect &
(c) Resource breakdown \\
\end{tabular}
\caption{Example domain categories and their original responses, 
redirects, and HTTPS usage for individual resource transfers.}
\label{fig:httpsDiff}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure*}[t]
\includegraphics[width=0.98\textwidth]{figures-mini-2x2-secure-response-redirect-ybar.pdf}
\caption{Secure connections for succesful connections when trying to use HTTPS.
(Note that the majority of websites (as per Figure~\ref{fig:httpsDiff}) do not respond.)}
\label{fig:https}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure*}[t]
\includegraphics[width=0.98\textwidth]{figures-mini-2x2-secure-response-redirect-ybar.pdf}
\caption{Secure connections for succesful HTTPS attempts (top row)
and HTTP attempts (bottom row).
(Note that the majority of websites does not respnd to HTTPS (as per Figure~\ref{fig:httpsDiff}).)}
\label{fig:https2}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure}[t]
\includegraphics[width=0.31\textwidth]{figures-mini-1x1-internal-resources-cdf.pdf}
\caption{External third-party resource usage.}
\label{fig:external}
\vspace{-0pt}
\end{figure}

@@

%%INSERT FIGURES (a) and (b) FROM THIS MORNINGS FIGURES ...
\begin{figure*}[t]
\includegraphics[width=0.98\textwidth]{figures-mini-2x2-categories-organizations-ybar.pdf}
\caption{Domain covererage of different categories of known tracker services (top row)
and companies (bottom row), as per Disconnect's blocking list.}
\label{fig:categories-companies}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{figures-mini-2x1-categories-scatter.pdf}
\begin{tabular}{cc}
(a) Sweden &
(b) Global \\
\end{tabular}
\caption{Correlation of tracker coverage seen with HTTP and HTTPS.}
\label{fig:scatter}
\vspace{-0pt}
\end{figure}
